# Interactive component


```{r, include=FALSE}
library(tidyr)
library(tidyverse)
library(ggplot2)
library(alr4)
library(dplyr)
library(hrbrthemes)
library("jsonlite")
```

turn the winning rate distribution in each rating graph into d3
```{r vectors-to-json, echo=FALSE, results="asis"}
temp <- read.csv("dataset/rank.csv")
cat(
  paste(
  '<script>
    var rankjs = ',toJSON(temp),';
  </script>'
  , sep="")
)
```
<div class="slidecontainer">
  <input type="range" min="1" max="5" value="3" class="slider" id="myRange">
  <p>Winning rates distribution on level <span id="demo"></span></p>
</div>


<script src="https://d3js.org/d3.v6.js"></script>
<div id="my_dataviz"></div>


<script>
var slider = document.getElementById("myRange");
var output = document.getElementById("demo");
output.innerHTML = slider.value; // Display the default slider value

// Update the current slider value (each time you drag the slider handle)
slider.oninput = function() {
  output.innerHTML = this.value;
}

var w = 500;
var h = 400;
var margin = {top: 10, right: 30, bottom: 30, left: 40},
    width = w - margin.left - margin.right,
    height = h - margin.top - margin.bottom;
var innerWidth = w - margin.left - margin.right;
var innerHeight = h - margin.top - margin.bottom;

// set the dimensions and margins of the graph


// append the svg object to the body of the page
var svg = d3.select("#my_dataviz")
  .append("svg")
    .attr("width", w)
    .attr("height", h)

svg.append("rect")
   .attr("x", 0)
        .attr("y", 0)
        .attr("width", w)
        .attr("height", h)
        .attr("fill", "white");

// X axis: scale and draw:
var xScale = d3.scaleLinear()
  .domain([0, 1]) 
  .range([0, width]);



var xAxis = d3.axisBottom()
  .scale(xScale);

var yAxis = d3.axisLeft()
  .scale(yScale);

var histogram = d3.histogram()
  .value(function(d) { return d.winning_rate; })   // I need to give the vector of value // then the domain of the graphic
  .thresholds(x.ticks(20)); // then the numbers of bins
// get the data
var bins = histogram(rankjs.filter(element => element.level == "level 3"));
var yScale = d3.scaleLinear()
  .domain([0, d3.max(bins)])
  .range([innerHeight, 0])


var bars = svg.append("g")
        .attr("id", "plot")
        .attr("transform", `translate (${margin.left}, ${margin.top})`)
        .selectAll("rect")
        .data(bins);

    bars.enter().append("rect")
        .attr("x", (d, i) => xScale(i))
        .attr("y", d => yScale(d))
        .attr("width", xScale.bandwidth())
        .attr("height", d => innerHeight - yScale(d))
        .attr("fill", "#69b3a2");

svg.append("g")
        .attr("class", "xAxis")
        .attr("transform", `translate (${margin.left}, ${h - margin.bottom})`)
        .call(xAxis);

svg.append("g")
        .attr("class", "yAxis")
        .attr("transform", `translate (${margin.left}, ${margin.top})`)
        .call(yAxis);

d3.select(".slidecontainer").select("#myRange")
  .on("click", function () {
    var slider = document.getElementById("myRange");
    if(slider.value == 1){ plot(rankjs, "level 1", 5)}
    else if(slider.value == 5){plot(rankjs, "level 5", 5)}
    else (plot(rankjs, "level "+slider.value,20))
})

var plot = function(data, tmplevel, nbin) {
    xScale.domain(d3.range(data.length));

    yScale.domain([0, d3.max(data)]);

  // And apply this function to data to get the bins
  var bars = histogram(data.filter(element => element.level == tmplevel));

   bars.enter()
          .append("rect")
            .attr("x", w)
            .attr("y", d => yScale(d))
            .attr("width", xScale.bandwidth())
            .attr("height", d => innerHeight - yScale(d))
            .attr("fill", "#69b3a2")
          .merge(bars)
            .transition()
            .duration(dur)
            .ease(d3.easeLinear)
            .attr("x", (d, i) => xScale(i))
            .attr("y", d => yScale(d))
            .attr("width", xScale.bandwidth())
            .attr("height", d => innerHeight - yScale(d))
  
  bars.exit().remove();
  // Y axis: scale and draw:
  svg.select(".xAxis")
            .transition()
            .duration(dur)
            .ease(d3.easeLinear)
            .call(xAxis);
 svg.select(".yAxis")
            .transition()
            .duration(dur)
            .ease(d3.easeLinear)
            .call(yAxis);


}


</script>