# Interactive component


```{r, include=FALSE}
library(tidyr)
library(tidyverse)
library(ggplot2)
library(alr4)
library(dplyr)
library(hrbrthemes)
library("jsonlite")
```

turn the winning rate distribution in each rating graph into d3
```{r,echo=FALSE, results="asis"}
# get clean dataset
data <- read.csv("dataset/rank.csv")
cat(
  paste(
  '<script>
    var rankjs = ',toJSON(rank),';
  </script>'
  , sep="")
)
```
<script src="https://d3js.org/d3.v6.js"></script>
<div id="my_dataviz"></div>


<script>

min = 0.0;
max = 1.0;
domain = [min,max];

var margin = { top: 30, right: 30, bottom: 30, left: 50 },
  width = 460 - margin.left - margin.right,
  height = 400 - margin.top - margin.bottom;
 
// The number of bins 
Nbin = 10;
var x = d3
  .scaleLinear()
  .domain(domain) 
  .range([0, width]);

var histogram = d3
  .histogram()
  .domain(x.domain()) // then the domain of the graphic
  .thresholds(x.ticks(Nbin)); // then the numbers of bins
 
// And apply this function to data to get the bins
var bins = histogram(data).value(fucntion(d){return d.winning_rate})

var svg = d3
  .select("body")
  .append("svg")
  .attr("width", width + margin.left + margin.right)
  .attr("height", height + margin.top + margin.bottom)
  .append("g")
  .attr("transform", "translate(" + margin.left + "," + margin.top + ")");

svg
  .append("g")
  .attr("transform", "translate(0," + height + ")")
  .call(d3.axisBottom(x));

var y = d3
  .scaleLinear()
  .range([height, 0])
  .domain([
    0,
    d3.max(bins, function(d) {
      return d.length;
    })
  ]); 
 
svg.append("g").call(d3.axisLeft(y));

svg
  .selectAll("rect")
  .data(bins)
  .enter()
  .append("rect")
  .attr("x", 1)
  .attr("transform", function(d) {
    return "translate(" + x(d.x0) + "," + y(d.length) + ")";
  })
  .attr("width", function(d) {
    return x(d.x1) - x(d.x0) - 1;
  })
  .attr("height", function(d) {
    return height - y(d.length);
  })
  .style("fill", "#69b3a2");
</script>